MaxEnt: What is it good for?

### 2015-07-03 ms.tex
grid
Tables
Grid has meaning

\documentclass[a4paper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}

@@

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{color, colortbl}

\definecolor{Gray}{gray}{0.5}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}

@@

The prior probabilities can also be laid out in a grid:

\begin{center}
\begin{tabular}{|ccc|}
\hline
0.059 & 0.167 & 0.117\\
0.048 & 0.076 & 0.231\\
0.030 & 0.082 & 0.191\\
\hline
\end{tabular}
\end{center}

Updating using MaxEnt, using the same constraint as before, is equivalent
to ruling out the first two rows of this grid and maintaining the third.
\begin{center}
\begin{tabular}{|ccc|}
\hline
\rowcolor{Gray}
0.059 & 0.167 & 0.117\\
\rowcolor{Gray}
0.048 & 0.076 & 0.231\\
0.030 & 0.082 & 0.191\\
\hline
\end{tabular}
$\Longrightarrow$
\begin{tabular}{|ccc|}
\hline
0.000 & 0.000 & 0.000\\
0.000 & 0.000 & 0.000\\
0.099 & 0.270 & 0.630\\
\hline
\end{tabular}
\end{center}

In Bayesian inference, we usually want to infer the value of a parameter
$\theta$ from the value of a datum $D$. Suppose there are three possible
$\theta$ values ($\theta_1$, $\theta_2$, and $\theta_3$) and three possible
$D$ values ($D_1$, $D_2$, and $D_3$). Then the hypothesis space
consists of nine propositions, created using logical {\bf and}; these
propositions are all of the form
$(\theta = \theta_i) \wedge (D = D_j)$ where $i, j \in \{1, 2, 3\}$.
